Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-15 VMCAI-revised-version/final.tex
effectivity

Executions of Minsky machines can be simulated by reset-VASS~\cite{araki1976PN}. 
Reset-VASS extend the basic VASS model with special “reset
transitions” that set to $0$ some coordinates in the vector. Let us recall their definition here.

It is well known that reset-VASS are WSTS~\cite{dufourd1998reset}. 
Since reset-VASS can simulate executions of a Minsky machine, {\sc Resilience} is undecidable for reset-VASS and hence for WSTS in general as well.\alain{déjà dit avant en mieux omega2 et strong comp et post-effective}\qed
\end{proof}

Remark we did not make use of the
property $\Bad$ complement of $\Safe$, simply 
$\Bad=\uparrow \Bad$ and $\Safe=\downarrow \Safe$, thus 
the above results still hold in the more general case where $\Bad$ and $\Safe$ are not complements of each others.

>>>>

Executions of Minsky machines can be simulated by reset-VASS~\cite{araki1976PN}~\cite{dufourd1998reset}. 
Reset-VASS extend the basic VASS model with special “reset
transitions” that set to $0$ some coordinates in the vector. 
%			Let us recall their definition here.

%      	it is well known that reset-VASS are WSTS~\cite{dufourd1998reset}. 
Since reset-VASS can simulate executions of a Minsky machine, {\sc Resilience} is undecidable for reset-VASS and hence for $\omega^2$-WSTS as well.\alain{déjà dit avant en mieux omega2 et strong comp et post-effective}\qed
\end{proof}

Remark we did not make use of the
property $\Bad$ complement of $\Safe$, simply 
$\Bad=\uparrow \Bad$ and $\Safe=\downarrow \Safe$, thus 
the above results still hold in the more general case where $\Bad$ and $\Safe$ are not complements of each others.\\
